Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome

### 2016-07-11 submission/supp_text.Rmd
Respond to reviewer's comments and edit text accordingly

This search yielded a total of 187 manuscripts.  From two previous other reviews of obesity and the bacterial microbiome along with knowledge of two other published papers that investigated obesity but were missed by the database search we obtained a total of 7 more articles.  We also had access to normal healthy individuals from an unpublished dataset.  This brought our total number of records to 196.

>>>>

This search yielded a total of 187 manuscripts.  From two previous other reviews of obesity and the bacterial microbiome along with knowledge of two other published papers that investigated obesity but were missed by the database search we obtained a total of 10 more articles. We also had access to normal healthy individuals from an unpublished dataset. This brought our total number of records to 197.
